### 2019-03-09 Thesis_Latex/Thesis/Chapter3/Chapter3.tex
update thesis

MPC is typically formulated in the state space. For a given discrete linear time-invariant (LTI) system:
\begin{equation}
\label{eqn:MPC_plant_discrete}
\vec{x}(k+1)=\vec{A}\vec{x}(k)+ \vec{B} \vec{u}(k)
\end{equation}
where $\vec{x}(k)\in\mathbb{R}^n$, $\vec{u}(k)\in\mathbb{R}^m$ are the state and the input, respectively. The central idea in the Model Predictive Control is to minimize some cost function, while still ensuring that some constraints are fulfilled. The generic MPC problem can be written as follows:
\begin{equation}
\label{eqn:MPC_optimization}
\begin{aligned}
& \underset{\textbf{u}}{\text{minimize}}
& & J(\vec{x}(k), \textbf{u}) \\
& \text{subject to}
& & \vec{x}_{k+i+1} = \vec{A}\vec{x}_{k+i}+ \vec{B} \vec{u}_{k+i}\quad\forall i=0,\dots N-1;\\
& & & \vec{x}_{k+i}\in \mathbb{X}\quad\forall i=0,\dots N-1;\\
& & & \vec{u}_{k+i}\in \mathbb{U}\quad\forall i=0,\dots N-1;\\  
& & & \vec{x}_{k+N}\in \mathbb{X}_f;\quad\vec{x}_k = \vec{x}(k).
\end{aligned}
\end{equation}
where $\textbf{u}=(\vec{u}_k,\dots,\vec{u}_{k+N-1})$ is a sequence of control inputs, $\vec{x}_{k+i}$ is the state at time $k+i$ as predicted at time $k$, and $N$ is the prediction horizon. The sets $\mathbb{X}\in\mathbb{R}^n$ and $\mathbb{U}\in\mathbb{R}^m$ define the constraints on the state and the input, respectively. Finally, the set $\mathbb{X}_f\subseteq\mathbb{X}$ defines the terminal constraint on the state. If we consider a regulation problem, the system \ref{eqn:MPC_plant_discrete} should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
\begin{equation}
\label{eqn:MPC_cost_function_regulation}
	J(\vec{x}(k), \textbf{u}) = \vec{x}^\intercal_{k+N}\vec{P}_f\vec{x}_{k+N}+\sum_{i=1}^{N}\vec{x}^\intercal_{k+i}\vec{Q}\vec{x}_{k+i}+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{equation}
where $\vec{P}_f,\vec{Q}\geq0$ (positive semi-definite) and $\vec{R}>0$ (positive definite) are weighting matrices.

Instead if we consider a servo problem, like tracking of a reference signal, the cost function is changed as follows:
\begin{equation}
\label{eqn:MPC_cost_function_servo}
\begin{aligned}
J(\vec{x}(k), \textbf{u})=& (\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})^\intercal\vec{P}_f(\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})\\
&+\sum_{i=1}^{N}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})^\intercal\vec{Q}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{aligned}
\end{equation}
where $\vec{x}^\text{ref}_{k+i}$, $\vec{x}^\text{ref}_{k+N}$ describe the reference trajectory. The standard MPC algorithm can be summarized by the following steps:
\begin{algorithm}%[b]
	\caption{Basic Model Predictive Control loop}
	\small
	\begin{algorithmic}[1]
		\State Measure the current state $\vec{x}(k)$;
		\State Solve the optimization problem \ref{eqn:MPC_optimization} with $\vec{x}(k)$ as initial state, where $\vec{u}(k)$ is calculated;
		\State Apply the first control of the optimal control sequence;
		\State Wait one sampling time and repeat steps 1-3;
	\end{algorithmic}
	\label{alg:rightOvertaking}
\end{algorithm}

>>>>

MPC is typically formulated in the state space. For a given discrete linear time-invariant (LTI) system:
\begin{equation}
\label{eqn:MPC_plant_discrete}
\vec{x}(k+1)=\vec{A}\vec{x}(k)+ \vec{B} \vec{u}(k)
\end{equation}
where $\vec{x}(k)\in\mathbb{R}^n$, $\vec{u}(k)\in\mathbb{R}^m$ are the state and the input, respectively. The central idea in the Model Predictive Control is to minimize some cost function, while still ensuring that some constraints are fulfilled. The generic MPC problem can be written as follows:
\begin{equation}
\label{eqn:MPC_optimization}
\begin{aligned}
& \underset{\textbf{u}}{\text{minimize}}
& & J(\vec{x}(k), \textbf{u}) \\
& \text{subject to}
& & \vec{x}_{k+i+1} = \vec{A}\vec{x}_{k+i}+ \vec{B} \vec{u}_{k+i}\quad\forall i=0,\dots N-1;\\
& & & \vec{x}_{k+i}\in \mathbb{X}\quad\forall i=0,\dots N-1;\\
& & & \vec{u}_{k+i}\in \mathbb{U}\quad\forall i=0,\dots N-1;\\  
& & & \vec{x}_{k+N}\in \mathbb{X}_f;\quad\vec{x}_k = \vec{x}(k).
\end{aligned}
\end{equation}
where $\textbf{u}=(\vec{u}_k,\dots,\vec{u}_{k+N-1})$ is a sequence of control inputs, $\vec{x}_{k+i}$ is the state at time $k+i$ as predicted at time $k$, and $N$ is the prediction horizon. The sets $\mathbb{X}\in\mathbb{R}^n$ and $\mathbb{U}\in\mathbb{R}^m$ define the constraints on the state and the input, respectively. Finally, the set $\mathbb{X}_f\subseteq\mathbb{X}$ defines the terminal constraint on the state. If we consider a regulation problem, the system (\ref{eqn:MPC_plant_discrete}) should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
\begin{equation}
\label{eqn:MPC_cost_function_regulation}
	J(\vec{x}(k), \textbf{u}) = \vec{x}^\intercal_{k+N}\vec{P}_f\vec{x}_{k+N}+\sum_{i=1}^{N}\vec{x}^\intercal_{k+i}\vec{Q}\vec{x}_{k+i}+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{equation}
where $\vec{P}_f,\vec{Q}\geq0$ (positive semi-definite) and $\vec{R}>0$ (positive definite) are weighting matrices.

Instead if we consider a servo problem, like tracking of a reference signal, the cost function is changed as follows:
\begin{equation}
\label{eqn:MPC_cost_function_servo}
\begin{aligned}
J(\vec{x}(k), \textbf{u})=& (\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})^\intercal\vec{P}_f(\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})\\
&+\sum_{i=1}^{N}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})^\intercal\vec{Q}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{aligned}
\end{equation}
where $\vec{x}^\text{ref}_{k+i}$, $\vec{x}^\text{ref}_{k+N}$ describe the reference trajectory. The standard MPC algorithm can be summarized by the following steps:
\begin{algorithm}%[b]
	\caption{Basic Model Predictive Control loop}
	\small
	\begin{algorithmic}[1]
		\State Measure the current state $\vec{x}(k)$;
		\State Solve the optimization problem \ref{eqn:MPC_optimization} with $\vec{x}(k)$ as initial state, where $\vec{u}(k)$ is calculated;
		\State Apply the first control of the optimal control sequence;
		\State Wait one sampling time and repeat steps 1-3;
	\end{algorithmic}
	\label{alg:MPCloop}
\end{algorithm}
